Enrich the datasets with new columns.

### 2020-08-22 inst/analysis/enrich_dataset.Rmd
Splitting and summarizing the dataset correctly

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

source("inc/latextags.R")
create_tags(path("/var/lib/R/project-evalR/revalstudy/data", "analysisStable.tex"), prefix="", default=TRUE)
```

@@

```{r eval_in_base}
eval_base_functions <- c("autoload", "autoloader", "bquote", "by.default", "by.data.frame", "invokeRestartInteractively", "Ops.data.frame", "dget", 
                         "eval", "eval.parent", "evalq", "local", "with.default", "within.data.frame", "within.list", "replicate", "subset.data.frame",
                         "subset.matrix", "transform.data.frame", "match.arg", "char.expand", "max.col", "parseNamespaceFile", "source", "sys.source",
                         "stopfinot", "as.data.frane.table", "match.fun", "trace", "untrace", ".doTrace")
```

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(params$data_filepath) %>%
    as_tibble()

eval_calls <- eval_calls_raw %>% filter(!caller_function %in% eval_base_functions)
```

There are so many calls that are similar:
```{r}
eval_calls_base <- eval_calls_raw %>% filter(caller_function %in% eval_base_functions) 
```

Let's remove the duplicate ones (but keep their numbers):

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
eval_calls <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
```

```{r}
eval_calls_base <- eval_calls_base %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)

eval_calls <- eval_calls %>% 
    mutate(eval_call_package = extract_package_name(eval_call_srcref, file)) %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r}
#eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "deduplicated_calls.fst"))

write_fst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))
```

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/calls.fst"
  data_kagglepath: "/var/lib/R/project-evalR/kaggle-korpus/run/titanic/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

source("preprocess.R", local = knitr::knit_global())
```

@@

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(params$data_filepath) %>%
    as_tibble() %>%
    mutate(corpus = "cran")

eval_calls_kaggle_raw <- 
  read_fst(params$data_kagglepath) %>%
  as_tibble() %>% 
  mutate(corpus = "kaggle")

eval_calls_raw <- bind_rows(eval_calls_raw, eval_calls_kaggle_raw)
```

```{r deduplicate}
eval_calls <- eval_calls_raw %>% deduplicate()
```

```{r add_types}
eval_calls <- eval_calls %>% add_types()
```

```{r add_source}
eval_calls <- eval_calls %>% add_eval_source() %>% add_eval_source_type()
```

```{r parse_args}
eval_calls <- eval_calls %>% add_parse_args()
```

```{r separate_datasets}
eval_calls_core <- eval_calls %>% filter(eval_source_type == "core")
eval_calls_packages <- eval_calls %>% filter(eval_source_type %in% c("package", "<undefined>") )
eval_calls_kaggle <- eval_calls %>% filter(eval_source_type == "kaggle")
```

```{r}
eval_calls_raw <- eval_calls_raw %>% select(-ends_with("_type")) %>% left_join(eval_calls)
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "raws.fst"))

write_fst(eval_calls_core, paste0(params$data_dirpath, "summarized-core.fst"))

write_fst(eval_calls_packages, paste0(params$data_dirpath, "summarized-packages.fst"))

write_fst(eval_calls_kaggle, paste0(params$data_dirpath, "summarized-kaggle.fst"))
```
